\begin{recipe}{Chicken Curry}
\introduction{The secret is really browning the onions... I mean really browning. And adding enough water!}
\ingredients{
\ingredient{\unit[2]{kg}}{chicken thighs, cut into 2 inch peices}
\ingredientsubtitle{initial fry}
\ingredient{\unit[3]{tbsp}}{corriander seeds}
\ingredient{\unit[3]{tsp}  }{mustard seeds}
\ingredient{}{corn, rapeseed oil or ghee}

\ingredient{6-8}{ onions, chopped }

\ingredient{\unit[4]{in}  }{ginger, blended}
\ingredient{1.5 bulbs}{garlic}
\ingredientsubtitle{spices added to onions}
\ingredient{\unit[1.5]{tsp}}{chilli flakes}
\ingredient{\unit[1]{stp}}{fenugreek}
\ingredient{\unit[3]{tsp}}{garam masala}
\ingredient{\unit[1.5]{tsp}}{chilli flakes}
}

\preperation{
\step In dry hot pan heat coriander seeds until they smoke.
\step Add mustard seeds, then within less than 30 seconds add oil (lots 2-3 iches ish if a \unit[1]{L} bottle) or Ghee.
\step Turn down to a medium heat, and once the oil is hot add chopped onions, tending to every 3-5 mins until caramelised and very dark brown.
\step Add ginger and garlic and cook for 5 minutes until light brown (do not burn the garlic!).
\step add turmeric, chilli flakes, fenugreek seeds, cumin, corriander, salt, garam masala, stir and fry for 3-5 mins. If  you can still see powder, the onion/spice mix is too dry so you should add more oil.
\step Add then chicken and fry for 25 mins until cooked, you can add some water at this point if the pan starts to dry out/the onions are in danger of burning. During this process add the tomatoes.
\step Before serving add 3-4 finely chopped green chillis (for a mild curry, more for a spicy one).
}
\end{recipe}