\begin{recipe}{Prawn Saganaki}
\introduction{The prawns! You can make the sauce ahead of time - it only gets better with time.}
\ingredients{
\ingredient{20}{large raw shell on prawns}
\ingredient{\unit[200]{g}}{barrel-aged feta}
\ingredientsubtitle{Sauce}

\ingredient{\unit[6]{tbsp}}{good olive oil}
\ingredient{1.5}{red onion, finely chopped}
\ingredient{3}{garlic cloves, crushed}
\ingredient{\unit[7]{cm}}{fresh ginger, grated}
\ingredient{\unit[0.5]{tsp}}{Aleppo chill flakes}
\ingredient{\unit[500]{g}}{tomato passata}
\ingredient{\unit[70]{g}}{black pitted olives}
\ingredient{7}{sun dried tomatoes}
\ingredient{\unit[1.5]{tsp}}{dried oregano}
\ingredient{\unit[1.5]{tsp}}{sugar}

\ingredientsubtitle{To finish}
\ingredient{handful}{basil leaves}
\ingredient{2 sprigs}{mint}
\ingredient{1}{lemon}
}
\preperation{
\step Heat the oven to 200\textcelcius. In advance devein the prawns if you wish (this is not essential).
\step On the hob, heat olive oil in a large oven-proof dish. Gently cook the onion, garlic, and ginger with a pinch of salt until softened.
\step Add the passata, olives, sun-dried tomatoes, sugar and chilli flakes. Season, and add a little water.
\step Transfer to the oven and cook the sauce for around an hour. The longer you leave it the better. Cook in the oven uncovered, checking and stirring frequently and stir any browned bits into the sauce, but cover if it starts to burn. Add more water if required. 
\step  Taste frequently, the sauce should go from being bitter and acidic from the onions and tomatoes, to being sweet and rich as they break down. Season to taste with salt and pepper. Once you reach this point, the sauce is done; at this point you can if you wish put the sauce in the fridge to use later.
\step When 15 minutes away from serving add the raw prawns, and top with the feta (first reheating the sauce if made in advance)
\step Cook the prawns for 12-15 minutes (longer if using more prawns), until the prawns are cooked and the feta has a golden brown tinge.
\step Once done, squeese in the lemon juice, top with the herbs, black pepper, and serve.
}
\end{recipe}